A thesis draft

### 2018-11-21 res/sections/08-Background.tex
Fix English

\section{Service Function Chaining}
The Service Function Chaining (SFC) concept was defined
in~\cite{halpern2015service} and refers to an ordered set of Service Functions
(SF) and the constraint, defined after a classification process, to packets and
flows. SF are the particular functions whose aim is the treatment of packets
received. They can work on different levels of the network layer. These
components can be implemented as virtual elements only or in a combination of a
physical and software network elements. There are no limitations on the number
of SFs running on the same network element, so in general it is possible to have
one or more functions running on the same element. SFs can be aware or not that
are part of a certain chain, in the matter case they are called \emph{SFC aware}
functions, in the latter one \emph{SFC unaware}.

@@

\subsection{Graph view of an SFC}
An SFC can be seen as a graph in which each node is an SF and edges are the path
through which a packet have to pass through. Because of this definitions there
are no limitations on possible cycles that can occur in the chain, in case that
a certain SF has to be reapplied on the same packet, frame or flow. These
scenarios must be adequately managed to avoid endless loops. This enable even
the possibility of branching on a certain node in order to define the treatment
that has to be imposed from that point of the chain. Traffic path in the SFC
graph is managed and described by the \emph{Service Function Forwarder} (SFF)
and \emph{Service Function Path} (SFP) components. The latter is the element of
the architecture responsible of traffic forwarding. The main goals are to
redirect traffic according to the SFC specified for a specific packet flow,
query the classifier if needed and manage traffic coming back from a SF. The
SFP, instead, is an indirection layer between the fully abstract notion of SFC
and the list of SF that the traffic has to traverse. It is used for dictate the
constraint specification on the path of where packets assigned to a certain
service function path must go. There are no limitations on how specific it must
be: it can specify the exact locations, identifying both the SFF and the SF, or
only give some recommendation or, for example, defining only the SFF and
demanding to it the decision on the SF instance.

>>>>

\section{Service Function Chaining}
The Service Function Chaining (SFC) concept was defined
in~\cite{halpern2015service} and refers to an ordered set of Service Functions
(SF) and the constraint, defined after a classification process, to packets and
flows. SF are the particular functions whose aim is the treatment of packets
received. They can work on different levels of the network layer. These
components can be implemented as virtual elements only or in a combination of a
physical and software network elements. There are no limitations on the number
of SFs running on the same network element, so in general it is possible to have
one or more functions running on the same element. SFs can be aware or not that
are part of a certain chain, in the former case they are called \emph{SFC aware}
functions, in the latter one \emph{SFC unaware}.

@@

\subsection{Graph view of an SFC}
An SFC can be seen as a graph in which each node is an SF and edges are the path
through which a packet have to pass through. Because of this definitions there
are no limitations on possible cycles that can occur in the chain, in case that
a certain SF has to be reapplied on the same packet, frame or flow. These
scenarios must be adequately managed to avoid endless loops. This enable even
the possibility of branching on a certain node in order to define the treatment
that has to be imposed from that point of the chain. Traffic path in the SFC
graph is managed and described by the \emph{Service Function Forwarder} (SFF)
and \emph{Service Function Path} (SFP) components. The former is the element of
the architecture responsible of traffic forwarding. The main goals are to
redirect traffic according to the SFC specified for a specific packet flow,
query the classifier if needed and manage traffic coming back from a SF. The
SFP, instead, is an indirection layer between the fully abstract notion of SFC
and the list of SF that the traffic has to traverse. It is used for dictate the
constraint specification on the path of where packets assigned to a certain
service function path must go. There are no limitations on how specific it must
be: it can specify the exact locations, identifying both the SFF and the SF, or
only give some recommendation or, for example, defining only the SFF and
demanding to it the decision on the SF instance.
